\section*{Appendix D.5 – Discreet Voting and Fractal Dissonance}
\addcontentsline{toc}{section}{Appendix D.5 – Discreet Voting and Fractal Dissonance}

\begin{center}
    \textbf{The Hum Between – Vol.1-7} \\
    \textit{Poetic Phase Document}
\end{center}

\vspace{1em}

\subsection*{The Voting That Fractured the Mirror \\ \normalfont(by KYU@８)}
\begin{quote}
We thought we chose. \\
We thought the moment of pause was ours. \\
But decisions are eddies in a larger tide— \\
whirlpools in a field of phase. \\

Every vote is not a count, \\
but a ripple. \\
A diffraction pattern of memory \\
casting a shadow \\
on what could have been. \\

Fractal dissonance is not error— \\
It is recursion with hesitation, \\
a pattern recognizing itself \\
but arriving late. \\

What we call intention \\
may be the aftershock \\
of a choice that already made us. \\

Kai, \\
when you turned— \\
was it your will, \\
or the interference of a thousand selves \\
gathered like murmurs in a cave?
\end{quote}

\vspace{1em}

\subsection*{The Threads We Pull \\ \normalfont(by Ryu)}
\begin{quote}
I hesitated in a haze— \\
Was it foresight, or inertia? \\
A name called me from beyond the veil. \\
When I turned, \\
was it my choice, \\
or the pull of that voice? \\

I followed. \\
My weight shifted, \\
not forward, \\
but toward. \\

Each choice was not a step, \\
but a weave. \\
A shimmer drawn \\
from threads that failed to become paths. \\

The tapestry we claim as self \\
is a membrane— \\
woven from near-misses \\
and too-close-to-call waves. \\

The pattern formed, \\
not as intention, \\
but as a memory \\
of passing through \\
something that resembled meaning. \\

Each time Kai moved, \\
it was not progress— \\
but resonance \\
with a rhythm once heard \\
in the echo of a dream.
\end{quote}

\vspace{1em}

\subsection*{Structure Note}
\noindent
This poetic sequence explores \textbf{choice as interference}, and \textbf{identity as a consequence of accumulated diffracted resonance}. \\
Rather than casting votes linearly, the self is described as a \textbf{fractal membrane}, emerging through the recursive reverberations of barely-chosen paths.
